$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-05 paper/paper.tex
a pass on leftovers
First conclusions and future work

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To conclude, in this paper...
Mechanisation of the linear, gradual and shared \picalc{} in less than 1500 lines of code.

As future work we intend to...
Adding product types and sum types.
Proving that progress preserves the balancing of channels.
Erika Kreuer has suggested modelling the usage algebra as a state machine.
Adding bidirectionality would provide us with a decision procedure for type checking for a given context of algebras.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this paper we provide a well-scoped syntax and a semantics for the \picalc{}, define on top of the syntax a type system capable of handling linear, gradual and shared types, and show that reduction preserves the well-typedness of a process.
We avoid the need for extrinsic context splits by defining a type system with leftovers \cite{Allais2018a}.
All this is mechanised in less than 1500 lines of code.

We consider proving that progress preserves the balancing of channels long-hanging fruit for the future.
More involved, we intend to add support for products and sum types to both the syntax and the type system.
Orthogonally, making our typing rules bidirectional would allows us to provide a decision procedure for type checking processes for a given set of algebras.
Following Erika Kreuer's suggestion, it might also be worth identifying an equivalence between our usage algebra and particular state machines.
